An Analysis on the Impact of Local Food Choices

### 2020-03-21 paper_knew.Rmd
Chanign bullets

Are the food source variables associated with the obesity rates in 2008/09?

@@

The following are the assumptions of linear regressions we used:
Independence: 
The county level data we used do not come froma simple rample sample. Thus we have to assume the independence in our data.

Normality:
We have county level observations of over 3000 rows. As this value is relatively large, the central limit theorem will take effect and the non-normality does not matter. We also checked the residual qq plot for normality.

Constant Variance for obesity rate:
We assess the plots of residuals vs fitted values of our linear models, and they show clear evidence of non-constant variance. The first plot is the residual plot for obesity rate in 2008/09, and the second plot is for obesity rate in 2013/14. There is clearly a pattern of residuals that is undesirable to us. We used robust standard error to try to correct the non-constant variance problem.

@@

#  Results
The results of our analyses for the five questions posed are detailed below.
### Are local food choices associated with the Obesity rates? 
###T-test result:
t = 58.258, df = 3136, p-value < 2.2e-16
alternative hypothesis: true difference in mean obesity rate between 2008 and 2013 is not equal to 0
95 percent confidence interval:
 1.285081 1.374594
mean of the differences = 1.329837

>>>>

## Are the food source variables associated with the obesity rates in 2008/09?

@@

The following are the assumptions of linear regressions we used:
 - Independence: 
The county level data we used do not come froma simple rample sample. Thus we have to assume the independence in our data. 
- Normality:
We have county level observations of over 3000 rows. As this value is relatively large, the central limit theorem will take effect and the non-normality does not matter. We also checked the residual qq plot for normality.  
- Constant Variance for obesity rate:
We assess the plots of residuals vs fitted values of our linear models, and they show clear evidence of non-constant variance. The first plot is the residual plot for obesity rate in 2008/09, and the second plot is for obesity rate in 2013/14. There is clearly a pattern of residuals that is undesirable to us. We used robust standard error to try to correct the non-constant variance problem.

@@

#  Results
The results of our analyses for the five questions posed are detailed below.

### Are local food choices associated with the Obesity rates? 
###T-test result:
t = 58.258, df = 3136, p-value < 2.2e-16
alternative hypothesis: true difference in mean obesity rate between 2008 and 2013 is not equal to 0
95 percent confidence interval:
 1.285081 1.374594
mean of the differences = 1.329837
